### 2023-07-14 python_excel_ite.tex
subsection notebook 2 pretty much done

A few design dilemmas are posed and some non-working approaches illustrated as we try to decide on how to implement an n-way data table function for this new object oriented model. These meta reflections are intentionally included to better mimic actual software development and reinforce the idea that software development is much more than simply writing code to implement a perfectly thought out design. We forge ahead with some preliminary ideas and are confronted with an intermediate problem related to generating a list of dictionaries that represent combinations of inputs, or \textit{scenarios}, to evaluate. This provides a great opportunity to remind students of one of the great strengths of the open source software ecosystem -- we can leverage work done in other packages and even look at actual source code to see how something was implemented. In this case, the well known scikit-learn package \cite{ScikitlearnMachineLearning} has a \code{ParameterGrid} function that solves our scenario generation problem quite nicely. This example also reminds the students of the value of being able to make sense of API documentation and of object oriented code written by others.

@@

Before trying to build our \code{goal\_seek} function we take a brief detour into basic root finding algorithms through packages like SciPy \cite{bibid} as well as in standalone Python scripts that are widely available in the Python data science ecosystem \cite{bibid}. We compare the output of Excel's Goal Seek with different starting values to the values obtained by different root finding algorithms implemented in Python. The importance of starting values and also the range of different root finding algorithms available is often surprising to business students who have spent most of their analytical life in Excel.

>>>>

A few design dilemmas are posed and some non-working approaches illustrated as we try to decide on how to implement an n-way data table function for this new object oriented model. These meta reflections are intentionally included to better mimic actual software development and reinforce the idea that software development is much more than simply writing code to implement a perfectly thought out design. We forge ahead with some preliminary ideas and are confronted with an intermediate problem related to generating a list of dictionaries that represent combinations of inputs, or \textit{scenarios}, to evaluate. This provides a great opportunity to remind students of one of the great strengths of the open source software ecosystem -- we can leverage work done in other packages and even look at actual source code to see how something was implemented. In this case, the well known \href{https://scikit-learn.org/stable/}{scikit-learn} package \cite{ScikitlearnMachineLearning} has a \code{ParameterGrid} function that solves our scenario generation problem quite nicely. This example also reminds the students of the value of being able to make sense of API documentation and of object oriented code written by others.

@@

Before trying to build our \code{goal\_seek} function we take a brief detour into basic root finding algorithms through packages like \href{https://docs.scipy.org/doc/scipy/tutorial/optimize.html#root-finding}{SciPy} \cite{SciPy} as well as in \href{https://github.com/patrickwalls/mathematical-python/}{open source notebooks and scripts} that are widely available in the Python data science ecosystem \cite{wallsMathematicalPython2023}. We compare the output of Excel's Goal Seek with different starting values to the values obtained by different root finding algorithms implemented in Python. The importance of starting values and also the range of different root finding algorithms available is often surprising to business students who have spent most of their analytical life in Excel.
